Improving the Image Acquisition Rate of an Atomic Force Microscope Through Compressive Sampling

### 2019-05-29 latex/afm-cs-main.tex
Rework nesta part.

\todo{This development is way too long!}
To mitigate these affects, we propose a new variant of BPDN that we term basis pursuit with
vertical variation (BPVV). BPVV adds a vertical total variation penalty in the spatial domain to the
optimization objective. That is, \eqref{op:bp} is modified to
\todo{It has been my observation that some benefit is gained by including $D_h$, but weighting it less than $D_v$. Not sure if we should leave it in. If so, BPVV should be BPTV or something.}
\begin{align}
  \min_{x\in Q_p}~f(x) &= \min_{x\in Q_p} \left\|U^Tx\right\|_1 + \alpha_v\left\|D_vx\right\|_1
                         + \alpha_h\left\|D_hx\right\|_1  \label{op:bp_tv}
  % \text{subject to} &\, \| R x - y \|_2 < \sigma,
\end{align}
where ${D_v x=\text{vec}(\nabla_v X)}$ (resp., ${D_v x=\text{vec}(\nabla_v X)}$) is the
discrete gradient in the vertical (resp., horizontal) direction (see, e.g., \cite[Section 6.1,]{becker_nesta_2011}). 
% and
% \begin{align*}
%   (\nabla_v X)_{i,j} = 
%   \begin{cases}
%     X_{i+1,j} - X_{i,j}, & 1\leq i<h,~ 1\leq j\leq s,\\
%     0, & \phantom{:}i=h,~\phantom{:::::} 1\leq j\leq s.
%   \end{cases}\\
%   (\nabla_h X)_{i,j} = 
%   \begin{cases}
%     X_{i,j+1} - X_{i,j}, & 1\leq i\leq h,~1\leq j<s \\
%     0, & \phantom{}1\leq i\leq,~\phantom{:::} j=s
%   \end{cases}
% \end{align*}
Thus, in \eqref{op:bp_tv}, $\left \| D_v x \right \|_1$ (resp., $\left \| D_h x \right \|_1$) is the total variation (TV) of the signal in the vertical (resp., horizontal) direction. The parameters $\alpha_v$ and $\alpha_h$ are weighting parameters.

The description of BPVV in \eqref{op:bp_tv} can be viewed as the combination of CS
and inpainting, in which the first term seeks a sparse solution while the
last two terms try to diffuse pixel information.
\todo{When written this way, it seems that BP+VV/TV can could also be interpreted in the frameowrk of overcomplete dictionaries?\cite{candes_redundant_2011}. }
To solve the optimization problem in \eqref{op:bp_tv} we use a (slight) extension to NESTA~\cite{becker_nesta_2011}. To that end, we re-write the cost $f(x)$ in \eqref{op:bp_tv} as
\begin{equation*}
  f(x) = \max_{u\in Q_d} \left\langle u, Wx \right\rangle,\quad Q_d = \{u:~||u||_{\infty} \leq 1\}
\end{equation*}
where
\begin{equation*}
W = \begin{bmatrix}U&\alpha_hD^T_h&\alpha_vD^T_v \end{bmatrix}^T.
%   W = \begin{bmatrix}U^T\\\alpha_hD_h\\\alpha_vD_v \end{bmatrix}.
\end{equation*}

>>>>

\todo{This development is way too long!}
To mitigate these affects, we propose a new variant of BPDN that we term basis pursuit with
vertical variation (BPVV). BPVV adds a vertical total variation penalty in the spatial domain to the
optimization objective. That is, \eqref{op:bp} is modified to
\todo{It has been my observation that some benefit is gained by including $D_h$, but weighting it less than $D_v$. Not sure if we should leave it in. If so, BPVV should be BPTV or something.}
\begin{align}
  \min_{x\in Q_p}~f(x) &= \min_{x\in Q_p} \left\|U^Tx\right\|_1
                         + \alpha\left\|D_vx\right\|_1
                         + \beta\left\|D_hx\right\|_1 \label{op:bp_tv}\\
                       &=\min_{x\in Q_p} \left\|Wx\right\|_1 \label{op:bp_tvW}
                         % \quad W = \begin{bmatrix}U&\alpha_hD^T_h&\alpha_vD^T_v \end{bmatrix}^T \nonumber
\end{align}
where
\begin{equation*}
W = \begin{bmatrix}U&\alpha_hD^T_h&\alpha_vD^T_v \end{bmatrix}^T
\end{equation*}
with ${D_v x=\text{vec}(\nabla_v X)}$ (resp., ${D_v x=\text{vec}(\nabla_v X)}$) representing a 
discrete gradient of a matrix in the vertical (resp., horizontal) direction (see, e.g., \cite[Section 6.1,]{becker_nesta_2011}). 
% and
% \begin{align*}
%   (\nabla_v X)_{i,j} = 
%   \begin{cases}
%     X_{i+1,j} - X_{i,j}, & 1\leq i<h,~ 1\leq j\leq s,\\
%     0, & \phantom{:}i=h,~\phantom{:::::} 1\leq j\leq s.
%   \end{cases}\\
%   (\nabla_h X)_{i,j} = 
%   \begin{cases}
%     X_{i,j+1} - X_{i,j}, & 1\leq i\leq h,~1\leq j<s \\
%     0, & \phantom{}1\leq i\leq,~\phantom{:::} j=s
%   \end{cases}
% \end{align*}
Thus, in \eqref{op:bp_tv}, $\left \| D_v x \right \|_1$ (resp., $\left \| D_h x \right \|_1$) is the total variation (TV) of the signal in the vertical (resp., horizontal) direction.
The parameters $\alpha$ and $\beta$ are weighting parameters.
The description of BPVV in \eqref{op:bp_tvW} can be interpreted as changing our assumption of sparsity in the DCT basis to assuming sparsity in an overcomplete dictionary \cite{candes_redundant_2011}.
\todo{I believe this is correct: Sean/Yufan can you confirm or reject?}

Moreover, when written as \eqref{op:bp_tvW}, the problem is in a form that may be solved with to NESTA~\cite{becker_nesta_2011}. For completeness, we give an overview here.
To that end, we re-write the cost $f(x)$ in \eqref{op:bp_tvW} as
\begin{equation*}
  f(x) = \max_{u\in Q_d} \left\langle u, Wx \right\rangle,\quad Q_d = \{u:~||u||_{\infty} \leq 1\}.
\end{equation*}
